Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-24 write_up/mixfishsim_ecolmod.tex
text updates in response to JMG and JJP

\usepackage{enumitem}
\usepackage{comment}
% For track-changes
%\usepackage[draft]{changes}
\usepackage[final]{changes} %% to turn off changes
\definechangesauthor[color = red]{JM}
\definechangesauthor[color = blue]{PD}
\definechangesauthor[color = green!40!black]{JJ}
\definechangesauthor[color = purple]{CM}

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y},d}$ is the annual recruits in year $y$ and day $d$ for cell
$c$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} \cdot \left(1 -
	\mathrm{e}^{-(F_{c,d} + M_{c,d})}\right) \cdot B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch is the sum of
those across all fleets and vessels, $C_{c, d} =
\sum\limits_{fl=1}^{fl}\sum\limits_{v=1}^{v} E_{fl, v, c, d} \cdot Q_{fl} \cdot
D_{c, d}$ with $fl$ and $v$ the fleet and vessel respectively and
$E_{fl,v,c,d}$ and $Q_{fl}$ fishing effort and catchability of the gear, and
$D_{c,d}$ is the density of the population at the location fished. \\

@@

Recruitment is modelled as a function of adult biomass. In
\textit{MixFishSim}, it can either take the form of a stochastic Beverton-Holt
stock recruitment relationship, or a stochastic Ricker stock recruitment
relationship. The Beverton-Holt relationship is defined as\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, the stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases.

@@

The survey simulation was set up with a fixed gridded station design with 100
stations fished each year, starting on day 92 and ending on day 112 (5 stations
per day) with same catchability parameters for all populations ($Q_{p} = 1$).
This approximates a real world survey design with limited seasonal and spatial
coverage.

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits three different fishing grounds, each of them multiple times (Figure
\ref{fig:mv}(A)), while across several trips fishing grounds that are further
apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
areas where the highest revenue were experienced, as shown by Figure
\ref{fig:mv} (D), where several vessels tracks are overlaid on the revenue
field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$

@@

\section*{Abbreviations} Detail any unusual ones used.

\section*{Acknowledgements} those providing help during the research..

>>>>

\usepackage{enumitem}
\usepackage{comment}

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& \left(1 + \rho \right) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \left( \alpha_{d-1} \cdot
	R_{\tilde{y}(c)}\right) \right)
	\hspace{0.9cm} + \\
	& Wt_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y}(c) \right)}
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} \cdot \left(1 -
	\mathrm{e}^{-(F_{c,d} + M_{c,d})}\right) \cdot B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch is the sum of
those across all fleets and vessels, $C_{c, d} =
\sum\limits_{fl=1}^{FL}\sum\limits_{v=1}^{V} E_{fl, v, c, d} \cdot Q_{fl} \cdot
D_{c, d}$ with $fl$ and $v$ the fleet and vessel respectively and
$E_{fl,v,c,d}$ and $Q_{fl}$ fishing effort and catchability of the gear, and
$D_{c,d}$ is the density of the population at the location fished. \\

@@

Recruitment is modelled as a function of adult biomass. In
\textit{MixFishSim}, it can either take the form of a stochastic Beverton-Holt
stock recruitment relationship, or a stochastic Ricker stock recruitment
relationship. The Beverton-Holt relationship is defined as\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes. The stochastic Ricker form \citep{Ricker1954} is:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases.

@@

The survey simulation was set up with a fixed gridded station design with 100
stations fished each year, starting on day 92 and ending on day 112 (5 stations
per day) with same catchability parameter ($Q_{p} = 1$) for all populations $p$.
This approximates a real world survey design with limited seasonal and spatial
coverage.

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits three different fishing grounds, each of them multiple times (Figure
\ref{fig:mv}(A)), while across several trips fishing grounds that are further
apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
areas where the highest revenue were experienced, as shown by Figure
\ref{fig:mv} (D), where several vessels tracks are overlaid on the revenue
field, i.e. $$Rev_{c} = \sum^P_{p=1} B_{c,p} \cdot Q_{fl,p} \cdot Pr_{p}$$

@@
